---
title: "Group 8 Assignment 1"
author: "Group 8"
date: "4/16/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggpubr)
library(dplyr)
library(janitor)
library(here)
library(readxl)
```

## Load data - csv
## This is a Covid-19 vaccination dataset based on age and sex

```{r vaccinecoverage}
vaccoverage <- readr::read_csv(file = "https://health-infobase.canada.ca/src/data/covidLive/vaccination-coverage-byAgeAndSex.csv")
```

## Head

```{r pressure, echo=TRUE}
head(vaccoverage)
```

## Provide and introduction of your analysis in the .rmd files so that it can be 
## produced in the Output: 

```{r}
# In this assignment we will be working with the Covid-19 vaccination dataset based on age and sex. This dataset has been acquired from google database: 

# This analysis focuses on vaccination reach according to the age and sex of different provinces of Canada. This data is of 2021. 
```


## Print the Structure of your dataset:
```{r stucture}
str(vaccoverage)
```


## List the variables in your dataset:

```{r variables, echo=FALSE}
names(vaccoverage)
```


## Print the top 15 rows of your dataset:

```{r rows}
head(vaccoverage, n=15)
```






## Write a user defined function using any of the variables from the dataset:

```{r}
library(dplyr)
prenamefn <- function(x) {return(vaccoverage %>% filter(vaccoverage$prename==x))}
print(prenamefn("Newfoundland and Labrador"))
```


## Use data manipulation techniques and filter rows based on any logical criteria that exist in your dataset.


```{r}
library(dplyr)
vaccoverage %>% filter(sex=="f")
```


## Identify the dependent & independent variables and use reshaping techniques and create a new data frame by joining those variables from your dataset.

```{r reshaping}
vacnew = cbind(vaccoverage$week_end, vaccoverage$age,vaccoverage$sex)
vacnew = data.frame(vacnew)
str(vacnew)
```

## Remove missing values in your dataset 

```{r}
complete.cases(vaccoverage)
```


## Identify and remove duplicated data in your dataset 

```{r}
duplicated(vaccoverage)
distinct(vaccoverage)
```




## Reorder multiple rows in descending order 


```{r}
library(tidyverse)
vaccoverage %>% arrange(desc(vaccoverage))
```


## Rename some of the column names in your dataset.

```{r rename}
library(dplyr)
dplyr::rename(vaccoverage, pruid1 = pruid, prename1 = prename, prfname1 = prfname)
```


## Add new variables in your data frame by using a mathematical function (for e.g. – multiply an existing column by 2 and add it as a new variable to your data frame)


```{r}
vaccoverage$newcolumn <- vaccoverage$numtotal_1doserange * 2
str(vaccoverage)
```



## Create a training set using random number generator engine.


```{r}
rnorm(20)
runif(2, min = 0, max = 500)
```



## Print the summary statistics of your dataset.


```{r}
summary(vaccoverage)
```




## Use any of the numerical variables from the dataset and perform the following statistical functions.
## Mean 
## Median 
## Mode
## Range


```{r}
library(modeest)
mean(vaccoverage$pruid)
median(vaccoverage$pruid)
mode = mfv(vaccoverage$age)
print(mode)
range(vaccoverage$prfname)
```



## Plot a scatter plot for any 2 variables in your dataset

```{r}
library(ggplot2)
ggplot(data = vaccoverage, aes(x = numtotal_atleast1dose, y = prename, col_factor(vaccoverage$prfname)))+ geom_point()
```


## • Plot a bar plot for any 2 variables in your dataset


```{r}
vaccoverage$age = as.character(vaccoverage$age)
library(ggplot2)
ggplot(data = vaccoverage, aes(x = age, fill = factor(sex)))+geom_bar()
```



## Find the correlation between any 2 variables by applying least square linear regression model.


```{r}
vaccoverage$numtotal_1dose = as.numeric(vaccoverage$numtotal_1dose)
vaccoverage$prop_atleast1dose = as.numeric(vaccoverage$prop_atleast1dose)
ggscatter(vaccoverage, x = "numtotal_1dose", y = "prop_atleast1dose", add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson", xlab = "numtotal_1dose", ylab = "prop_atleast1dose")
```


